%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/drsamitha/Demo_DBMS}{Git Repo}} % sub entry 
    {Manage Different Databases By Single AI Platform} % topic
    {Django / Python / NOSQL / SQL / ORM / Docker / AI / FastAPI} %red title
    {2025} % second sub entry
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Manage relational and non relational databases use simple natural language.}
        \item {Python based cross--platform software for interact with the database.}
        \item {Support popular relational databases like PostgreSQL, MariaDB, Oracle, sqlite3, etc....}
        \item {Maintain MongoDB with support of third party plugin.}
        \item {Take advantages of ORM of the django framework for design single DB connection portal that support different databases.}
        \item {ML Ops skills for deploy backend AI platform.}
        \item {Deploy and maintain different database technologies.}
        \item {Collaborate with team for development and design system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/drsamitha/TodoAPI}{Git Repo}} % sub entry 
    {Todo App Backend} % topic
    {NestJS / Typescript / MongoDB / Docker / Swagger} %red title
    {2024} % second sub entry
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Backend CRUD operations as API endpoints.}
        \item {Containerized using Docker.}
        \item {Swagger documentations for endpoints.}
        \item {Deploy MongoDB as seperate docker in same network.}
      \end{cvitems}
    }
 
%---------------------------------------------------------
  \cventry
    {\href{https://github.com/drsamitha/adbLib}{Git Repo}} % sub entry 
    {Android ADB connection library} % topic
    {C++ / C / Boost / vcpkg / CMake / Doxygen} %red title
    {2024} % second sub entry
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Library for simplify Android devices ADB connection.}
        \item {Native cross platform support.}
        \item {Automate documentation generating process about usage of the library.}
        \item {Socket programming for computer networking.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {\href{https://github.com/drsamitha/Awesome-CV}{Git Repo}} % sub entry 
    {Automate Cv-Resume Publication} % topic
    {Latex / Git action / CI--CD} %red title
    {2025 -- present} % second sub entry
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automate github documents releases.}
        \item {Latex language for ducumentation.}
        \item {Version controling for different releases.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
